---
title: "dstask"
author: "George WIlloughby"
date: "16/10/2020"
output: html_document
---
# Importing the Cheshire outcomes data

```{r}
cheshire08 <- read.csv("2020-08-cheshire-outcomes.csv")
```

# Creating a summary of the first dataset.

```{r}
summary(cheshire08$Outcome.type)
```

```{r}
summary(cheshire08)
```

# Joining the July dataset

*This can be done using the same way as before*

```{r}
cheshire07 <- read.csv("2020-07-cheshire-outcomes.csv")
```

# Using Rbind() to connect the datasets

```{r}
cheshire07to08 <- rbind(cheshire07, cheshire08)
```

# Exporting the data

```{r}
write.csv(cheshire07to08, "cheshirejulytoaug.csv")
```

# Creating a subset

*I am going to filter the data to show the 'outcome type' as 'suspect charged'* 

*Also, remember to double-check the spelling of the outcome types. R is case sensitive.*

```{r}
cheshirecharged <- subset(cheshire07to08, cheshire07to08$Outcome.type == "Suspect charged")
```

*The new dataset is in the environment*

```{r}
library(dplyr)
```

#Filtering to show the count for 'Suspect charged'

```{r}
cheshirecharged %>% 
    filter(!is.na(Outcome.type)) %>% 
    group_by(Outcome.type) %>% 
    count()
```

# Show the count for each crime outcome

```{r}
cheshire07to08 %>% 
    filter(!is.na(Outcome.type)) %>% 
    group_by(Outcome.type) %>% 
    count()
```
# Visualising the data

```{r}
library(ggplot2)
```

```{r}
ggplot(cheshire08) +
  geom_bar(aes(x=Outcome.type))+
  labs(title = "Outcome Types in CE") +
  coord_flip()
```
*If anyone could help me with adjusting the x and y axis to make it look cleaner, that would be great*

*I looked online and saw the reorder() function but I couldn't quite work it out* 













