---
title: "westyorkyearly1920"
author: "George WIlloughby"
date: "14/12/2020"
output: html_document
---

# Import data

```{r}
westyorkshireyearly1920 <- read.csv("westyorkshireyearly.csv", stringsAsFactors = FALSE)

westyorkshireyearly1920
```

# Dropping columns

```{r}
library(dplyr)

westyorkshireyearly1920 <- westyorkshireyearly1920 %>%
  select(Type, Date, Age.range, Self.defined.ethnicity, Outcome)

westyorkshireyearly1920
```

# Renaming columns

```{r}
colnames(westyorkshireyearly1920) <- c("Type", "Date", "Age_range", "Ethnicity", "Outcome")

colnames(westyorkshireyearly1920)
```

# Cleaning the date

```{r}
library(tidyr)

cleanerdate <- tidyr :: separate(westyorkshireyearly1920, 2, c("Date"), sep = "T")

westyorkshireyearly1920 <- cleanerdate

westyorkshireyearly1920
```


# Counting and removing NAs

```{r}
westyorkshireyearly1920[westyorkshireyearly1920==""] <- NA

westyorkshireyearlyclean <- westyorkshireyearly1920 %>%
  drop_na(Age_range, Ethnicity)

westyorkshireyearlyclean %>%
  count(Ethnicity, Age_range, sort = TRUE)
```

# Total stop and searches where Ethnicity and age group could be identified


```{r}
table(westyorkshireyearlyclean$Type)
```

*There seems to be 12 additional values in the 'type' column'.*

```{r}
westyorkshireyearlyclean = filter(westyorkshireyearlyclean, Type != "Type")

table(westyorkshireyearlyclean$Type)
```

Now we can add together the search types to figure out the total of all ethnicities

```{r}
westyorkshireyearlyclean %>%
  count(Type)

totalwestyorkshire <- 6420 + 12869
```
# Removing ethncities

```{r}
install.packages("jsonlite")
install.packages("httr")

library(jsonlite)
library(httr)
```


```{r}
westyorkshireyearlyclean$Asian <- grepl("Asian/Asian British", westyorkshireyearlyclean$Ethnicity)
#Subset
westyorkshireyearlyclean <- subset(westyorkshireyearlyclean, westyorkshireyearlyclean$Asian == TRUE)

table(westyorkshireyearlyclean$Ethnicity)
```


```{r}
westyorkshireyearlyclean %>%
  count(Age_range, sort = TRUE)

# Proportion of total stop and searches

westyorktotalasian <- 2229 + 1408 + 530 + 488 + 1
```

## Asian proportion of total

```{r}
westyorktotalasian / totalwestyorkshire * 100
```


# Proportion of Asian stopped aged 10-24

```{r}
westyorkshireyearlyclean %>%
  count(Age_range, sort = TRUE)

westyorkasian1024 <- 530 + 2229
```

*10-24 proportion*

```{r}
westyorkasian1024 / westyorktotalasian * 100
```








