---
title: "wmyearly1920"
author: "George WIlloughby"
date: "09/12/2020"
output: html_document
---

# Importing the data

```{r}
wmstopandsearch10_19 <- read.csv("2019-10-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch11_19 <- read.csv("2019-11-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch12_19 <- read.csv("2019-12-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch01_20 <- read.csv("2020-01-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch02_20 <- read.csv("2020-02-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch03_20 <- read.csv("2020-03-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch04_20 <- read.csv("2020-04-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch05_20 <- read.csv("2020-05-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch06_20 <- read.csv("2020-06-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch07_20 <- read.csv("2020-07-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch08_20 <- read.csv("2020-08-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch09_20 <- read.csv("2020-09-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
wmstopandsearch10_20 <- read.csv("2020-10-west-midlands-stop-and-search.csv", stringsAsFactors = FALSE)
```

# Rbind ()

We are going to join the stop and search figures together to make one data set

```{r}
wmyearlyoct19to20 <- rbind(wmstopandsearch10_19, wmstopandsearch11_19, wmstopandsearch12_19,wmstopandsearch01_20,wmstopandsearch02_20, wmstopandsearch03_20,wmstopandsearch04_20, wmstopandsearch05_20, wmstopandsearch06_20,wmstopandsearch07_20, wmstopandsearch08_20, wmstopandsearch09_20, wmstopandsearch10_20)
```


#Renaming columns

```{r}
#Rename columns
colnames(wmyearlyoct19to20) <- c("Type", "Date", "Policing_operation_part", "Policing_operation", "Latitude", "Longitude", "Gender", "Age_range", "Ethnicity", "Officer_ethnicity", "Legislation", "Search_object", "Outcome", "Object_search_outcome", "Removal_of_clothing")
```

#Inspect the data

```{r}
head(wmyearlyoct19to20)
```

# Dropping unwanted columns

```{r}
#Activate packages
library(dplyr)

#Dropping columns
wmyearlyoct19to20 <- wmyearlyoct19to20 %>%
  select(Type, Date, Ethnicity, Age_range, Legislation, Search_object, Outcome, Removal_of_clothing)

wmyearlyoct19to20
```

# Changing the date

*The date we want is the YYYY/MM/DD*

```{r}
install.packages("tidyr")
```

```{r}
library(tidyr)
```

**Changing the date**

```{r}
#New date
newdate <- tidyr :: separate(wmyearlyoct19to20, 2, c("Date"), sep= "T")

newdate
```

*Putting the new date into the yearly dataset*

```{r}
wmyearlyoct19to20 <- newdate

wmyearlyoct19to20
```

# Analysis

We want to see the monthly figures for the number of Asians stopped and searched in the West Midlands Police Force area.

To do this, we will need to remove the other ethnicities.


```{r}
library(tidyverse)
```


```{r}
#Inspecting ethnicities

wmyearlyoct19to20 %>%
  count(Ethnicity, sort = TRUE)

```
# Calculating the NAs and then excluding them from the dataset

```{r}
wmyearlyoct19to20[wmyearlyoct19to20==""] <- NA

ethnicityyearly <- wmyearlyoct19to20 %>%
  drop_na(Ethnicity, Age_range)

ethnicityyearly %>%
  count(Ethnicity, Age_range, sort = TRUE)
```
```{r}
ethnicityyearly %>%
  count(Type)

totalstoppedwestmid <- 3545 + 16864

totalstoppedwestmid
```



# Export data

```{r}
write.csv(x=ethnicityyearly, file="westmidlandsethnicity.csv")
```

# Removing the unwanted ethnicities

```{r}
install.packages("jsonlite")
install.packages("httr")
```

```{r}
#Activating packages
library(jsonlite)
library(httr)
```


```{r}
ethnicityyearly$Asian <- grepl("[A]+", ethnicityyearly$Ethnicity)
#Subset
asian.ethnicity <- subset(ethnicityyearly, ethnicityyearly$Asian == TRUE)

asian.ethnicity
```

```{r}
asian_only <- grepl("Asian/Asian British", ethnicityyearly$Ethnicity)
```

```{r}
ethnicityyearly$Asian <- asian_only
```

```{r}
asian_only <- grepl("Asian/Asian British [A-s]", ethnicityyearly$Ethnicity)
```

```{r}
asian_only <- subset(ethnicityyearly, ethnicityyearly$Asian == TRUE)

table(asian_only$Ethnicity)
```

```{r}
write.csv(x=asian_only, file="wmethnicityandagegroups.csv")
```

```{r}
asian_only
```

```{r}
asian_only %>%
  count(Type)

asianstoppedwestmid <- 1438 + 4437
#1438 + 4437 = 5875

asianstoppedwestmid / totalstoppedwestmid * 100
```

```{r}
asian_only %>%
  count(Ethnicity, Age_range, sort = TRUE)
```

```{r}
asian_only %>%
  group_by(Age_range) %>%
  count(Age_range, sort = TRUE)
```


```{r}
909 + 2798

3707 / 5875 *100

#63% of those stopped and searched by West Midlands Police Force were between 10-24
```


```{r}

```








